\documentclass[a4paper, 10pt]{report}   % list options between brackets
\usepackage{fullpage}
\usepackage[utf8]{inputenc}            % list packages between braces
\usepackage[table]{xcolor}
\usepackage[english]{babel}%.................. Language setup
    \addto{\captionsenglish}{\renewcommand{\bibname}{References}}
% type user-defined commands here

\usepackage{graphicx}
\begin{document}

\title{ \fontsize{10mm}{25mm}\textbf{Use of Recommender System in Robotics}\\
		 \vspace{20 mm} 
		 {R\&D Project Proposal} \\
		}   % type title between braces




\author{\textbf{Deebul Nair} \\
			\textit{Matrikel number : 9023573}\\
					 \vspace{2 mm} 
			\textit{email : deebul.nair@smail.inf.h-brs.de}\\
					 \vspace{50 mm} 
		{B-IT Master Studies Autonomous Systems}\\
			{Advised by:}\\
			\textbf{Prof. Dr. Paul Pl{\"o}ger}\\
			\textbf{Iman Awaad}\\
		{University of Applied Sciences Bonn-Rhein-Sieg}
		}         % type author(s) between braces




\maketitle

\section*{Introduction}             % chapter 1
\begin{itemize}
	\item Decision making problem is a highly studied topic, especially in domain of autonomous decision making systems.
	\item There are several models and techniques for decision making in autonomous robots. Sequential Decision Making, Markov Decision process are some of the popular techniques.
	\item Decision making is a difficult problem because the agent has to search the complete state space to make an appropriate decision. This becomes extremely time consuming task, as the state space keeps on increasing.
	\item Also situation arises when the decision making has to be done with only partial knowledge of the state space.
\subsection*{Recommender systems}
\begin{itemize}
	\item Recommender systems are machine learning algorithms which produce a set of recommendations.
	\item Recommender systems are extremely popular in the web domain for recommending movies, news, books and products in general to online users.
	\item Recommender system are useful alternatives to search algorithms since they help users to discover item from an avalanche of items based on their preferences and needs.
	\item Since recommender system can learn from a huge data set of items to help recommend a item for the user, this can be utilized in decision making of robotics to learn from huge state space and recommend a proper decision to take.
\end{itemize}
\label{sub:}

	\item {My R\&D is to take this insight from recommender systems and adapt it to the analogous problem of making decision for robotics application.}
\subsection*{Recommender system in Learning by Demonstration}
\begin{itemize}
	\item Learning by demonstration is a an approach in which the robot learns tasks based on the demonstrations shown by the teacher.
	\item In general it is hard to infer which part of the demonstration the robot has to replicate.
	\item The recommender system can be used in such scenario to recommend the robot which all features from the action are important for reproducing the action.
\end{itemize}
\label{sub:}

\end{itemize}

% subsection  (end)

\section*{Related Work}
\begin{itemize}

\item In \cite{matikainen_model_2012}Matikainen  have applied this insight to develop a 
Model Recommendation which applied the approach to computer vision; which uses this 
collaborative filtering techniques as seen in recommender systems to recommend classifiers from 
a large library for a computer vision task.
\item In \cite{abdo_inferring_2014} Nichola Abdo et al. have applied this analogy to Learning from demonstration 
for robots.  It uses the content based filtering approach to deal with the identification 
of the relevant features that describe an action.
\item Recently \cite{matikainen_multi-armed_2013} Matikainen has applied  collaborative filtering as an alternative to 
multi task policy optimization. They investigate the problem of selecting a state 
machine from a library to control a robot.
\end{itemize}

\section*{Detailed Project Plan}
\begin{itemize}
	\item Study literature about Recommender System and Learning by Demonstration.
	\item List of available implementation of Recommender system which can be used for the project
	\item Understand mathematics model behind working of the Recommender system.
	\item Demonstration of application of Recommender system in the field of Learning by Demonstration
	\item Kinesthetic Demonstration $\Rightarrow$ Making test setup for collection of information for learning 
	\begin{itemize}
		\item Selection of libraries for image processing (Marker detection	)
		\item Recording kinematics of arm
		\item Or Collect data using simulation
	\end{itemize}
	\item Implement $\rightarrow$ Model building of an action
	\item Implement $\rightarrow$ Feature selection based on Model using Recommender system.
	\item Base Implementation of \emph{"Reaching for a specific Object"}
	\item Evaluate and Fine tune the above implementation
	\item Experiment with different sets of recommender systems
	\item Evaluate the results 
	\item Methodology of adapting the recommender system to other fields of robotics .
	\item Document the results in a R\&D report and optionally a paper.
	
\end{itemize}

\section*{Expected Results}
\begin{itemize}
	\item Methodology for the problem formulation (model building) of recommender systems in Robotics
	\item 1 Model build using recommender system for Manipulation
	\item Evaluation of results
\end{itemize}

\section*{Gantt Chart}

\begin{tabular}{|l|lllllllll|}
\hline
	Task & Dec15 & Jan & Feb & March & April & May & June & July & Aug15\\
\hline
	Literature Search & \cellcolor{green} & \cellcolor{green}& & & & & & & \\
\hline
	Data Collection &  & & & \cellcolor{green}& & & & & \\
\hline
	$1^{st}$ Model Implementation &  & & & \cellcolor{green}& \cellcolor{green}& & & & \\
\hline
	Recommender System &  & & & &\cellcolor{green} & \cellcolor{green}& & & \\
\hline
	Evaluation &  & & & & &\cellcolor{green} &\cellcolor{green} & & \\
\hline
	Documentation &  &\cellcolor{green}&\cellcolor{green} &\cellcolor{green} & \cellcolor{green}& \cellcolor{green}& \cellcolor{green}& \cellcolor{green}& \cellcolor{green}\\
\hline

\end{tabular}


\bibliography{RecommenderSystemInRobotics.bib}{}
\bibliographystyle{unsrt}
\end{document}

