\documentclass[a4paper]{report}
%Gummi|063|=)
\title{\textbf{RnD Meeting 3} \\
		Minutes for December 9-10, 2014}

\author{B-IT Master Studies Autonomous Systems\\
		University of Applied Sciences Bonn-Rhein-Sieg\\
		}
\date{}
\begin{document}

\maketitle

\section{Present}
\begin{itemize}
	\item Nair Deebul
	\item Awaad, Iman
\end{itemize}
\section{Discussed}
\begin{itemize}
	\item Deebul Presented his Detailed Project Plan for winter semester 2014. The Project Plan was discussed.
	\item Timeline of project was discussed in detail
	\item Expected Results were iterated. 
		\item Iman presented her ideas on a possible use case of Recommender system in Planning. Specifially on the use of recommender system in learning user preferences for robotics tasks .
		\item The idea that the RnD has to be more on the Methodology of the use of Recommender System in Robotics was emphazied. So the work has to also provide an overview of how the Recommender system can be used for other similar tasks.

\end{itemize}

\section{Approved Activities}
\begin{itemize}
	\item The RnD was named "Use of Recommender System in Robotics"
	\item Expected Results :
	\begin{itemize}
		\item Methodology for the problem formulation(i.e. Model building ) for use of recommender system in Robotics
		\item 1 Working Model build for the use case of "Learning from demonstration for Manipulation"
		\item Evaluation of results (eg : Results using different recommender system )

	\end{itemize}
	\item Proposed timeline was accepted . With changes in the start date of documentation and inclusion of vacation .
	\item Iman would provide a small writeup on her views on the possible problems in the field of Planning which can be addressed by Recommender system.
	\item Deebul will setup Github account for the RnD and the project activites will be tracked in the account.
\end{itemize}

\section{Next Meeting}
January, 2015 $1^{st}$ week
\end{document}
