\documentclass[a4paper]{report}
%Gummi|063|=)
\title{\textbf{RnD Meeting 1} \\
		Minutes for October 30, 2014}

\author{B-IT Master Studies Autonomous Systems\\
		University of Applied Sciences Bonn-Rhein-Sieg\\
		}
\date{}
\begin{document}

\maketitle

\section{Present}
\begin{itemize}
	\item Deebul Nair
	\item Prof. Dr. Paul G. Pl{\"o}ger
\end{itemize}
\section{Discussed}
\begin{itemize}
	\item Deebul Presented his RnD Proposal for winter semester 2014. Proposal was regarding application of Recommender System in Robotics. PhD Thesis of Pyry Matikainen was briefly discussed about similar application. Also University of Frieburgs application of the system in Robot Learning was discussed.
	\item Professor commented not to use the specific case of Recommender Systems. But to Generalize the idea of Recommender System (i.e. to completely understand the science behind the Recommender systems) and view the problem as a general Machine learning problem. Such that the Recommender System becomes 1 of the application of the generalized Machine learning.
	\item Based on this scientific knowledge behind Recommender System Deebul will Program a solution  for Robotics application and evaluate the results.

\end{itemize}

\section{Approved Activities}
\begin{itemize}
	\item Extending the Robot Learning experiment(From Univ Frieburg) for youBot and applying in Robocup as a use case to the RnD.
	\item Continue exploration for new areas in robotics application where the Recommender systems can be applied.
	\item Prof. Dr. Paul G. Pl{\"o}ger has agreed to be the advisor of Nair Deebul.
\end{itemize}

\section{Next Meeting}
To be decided.
\end{document}
