\begin{abstract}
   Learning from Demonstration covers methods by which a robot learns new skills
   using human guidance. Learning from Demonstration in robotic systems involves a
   number of important aspects, such as deducing the relevant features of the
   observations, modelling  based on the relevant features and execution
   based on the model. We consider the problem of inferring the pertinent
   features using a set of demonstrations, that should be reproduced by the
   robot. This is challenging because the number of demonstrations on which the
   learning has to be made are few. In this work, we improvise an approach which
   is inspired by recommender systems to have an expert knowledge base. This
   knowledge base is then used to recommend the relevant features to imitate .
   The expert knowledge base is a reduced subset of the whole search space of
   the features to be imitated. The key novelty  of our work is in the expert
   knowledge base used for recommendation, which is structured based on effect
   metrics. We argue that the structured knowledge base helps in inferring the
   relevant features using very less demonstrations. In this work we use the
   skill based framework for robot programming. Under this framework we try to
   learn the \textif{"move"} motion primitive. The relevant features for successful
   reproduction of the \textif{"move"} motion primitive are learnt using the method
   proposed. The approach was evaluated in simulation and using data acquired
   from the youBot robot. The results shows promising progress as it could
   learn with less number of demonstrations.
\end{abstract}
